Conversations in time: interactive visualization to explore structured temporal data

### 2020-07-27 tsibbletalk.Rmd
draft static seasonal plots

---
title: "Conversations in time: interactive visualization to explore structured temporal data"
author:
- name: Earo Wang
  affiliation: The Univeristy of Auckland
  address:
  - line 1
  - line 2
  email: earo.wang@auckland.ac.nz
- name: Dianne Cook
  affiliation: Monash Univeristy
  address:
  - line 1
  - line 2
  email: dicook@monash.edu
bibliography: references.bib
abstract: >
  An abstract of less than 150 words.
preamble: |
  % Any extra LaTeX you need in the preamble
output: rticles::rjournal_article
---

@@

* Time wrapping: absolute time to relative time, grouped by corresponding lower-resolution time. date-times -> hours, by dates
* Transform and send newly-transformed data via server, without updating anything else (e.g. layout and graphical elements), to avoid completely redrawing.
* A shiny module: slider and plot

>>>>

---
title: "Conversations in time: interactive visualization to explore structured temporal data"
author:
- name: Earo Wang
  affiliation: The Univeristy of Auckland
  address:
  - Department of Statistics
  - The Univeristy of Auckland
  - New Zealand
  email: earo.wang@auckland.ac.nz
- name: Dianne Cook
  affiliation: Monash Univeristy
  address:
  - Department of Econometrics and Business Statistics
  - Monash University
  - Australia
  email: dicook@monash.edu
bibliography: references.bib
abstract: >
  An abstract of less than 150 words.
preamble: |
  % Any extra LaTeX you need in the preamble
output: rticles::rjournal_article
---

@@

The other critical aspect of a tsibble is "index", that provides foundational temporal context. A common tool in time series analytical toolkit is seasonal plots that lay time series not on the whole time scale, but on an origin-less relative time unit, such as `gg_season()` in the {feasts} package. It helps to examine and emphasise periodic/aperiodic patterns, comparing to time series plots that primarily focus on trends. Standard seasonal plots break the overall time into two components: seasonal periods on the x-axis, and grouped by their corresponding lower-resolution time. For example, monthly data can be decomposed into months separated by years, and hourly data into hours grouped by days.

* Transform and send newly-transformed data via server, without updating anything else (e.g. layout and graphical elements), to avoid completely redrawing.
* A shiny module: slider and plot

### 2020-07-27 tsibbletalk.tex
draft static seasonal plots

\begin{itemize}
\tightlist
\item
  Time wrapping: absolute time to relative time, grouped by
  corresponding lower-resolution time. date-times -\textgreater{} hours,
  by dates
\item
  Transform and send newly-transformed data via server, without updating
  anything else (e.g.~layout and graphical elements), to avoid
  completely redrawing.
\item
  A shiny module: slider and plot
\end{itemize}

@@

\address{%
Earo Wang\\
The Univeristy of Auckland\\
line 1\\ line 2\\
}
\href{mailto:earo.wang@auckland.ac.nz}{\nolinkurl{earo.wang@auckland.ac.nz}}

\address{%
Dianne Cook\\
Monash Univeristy\\
line 1\\ line 2\\
}
\href{mailto:dicook@monash.edu}{\nolinkurl{dicook@monash.edu}}

>>>>

The other critical aspect of a tsibble is ``index'', that provides
foundational temporal context. A common tool in time series analytical
toolkit is seasonal plots that lay time series not on the whole time
scale, but on an origin-less relative time unit, such as
\texttt{gg\_season()} in the \{feasts\} package. It helps to examine and
emphasise periodic/aperiodic patterns, comparing to time series plots
that primarily focus on trends. Standard seasonal plots break the
overall time into two components: seasonal periods on the x-axis, and
grouped by their corresponding lower-resolution time. For example,
monthly data can be decomposed into months separated by years, and
hourly data into hours grouped by days.

\begin{itemize}
\tightlist
\item
  Transform and send newly-transformed data via server, without updating
  anything else (e.g.~layout and graphical elements), to avoid
  completely redrawing.
\item
  A shiny module: slider and plot
\end{itemize}

@@

\address{%
Earo Wang\\
The Univeristy of Auckland\\
Department of Statistics\\ The Univeristy of Auckland\\ New Zealand\\
}
\href{mailto:earo.wang@auckland.ac.nz}{\nolinkurl{earo.wang@auckland.ac.nz}}

\address{%
Dianne Cook\\
Monash Univeristy\\
Department of Econometrics and Business Statistics\\ Monash
University\\ Australia\\
}
\href{mailto:dicook@monash.edu}{\nolinkurl{dicook@monash.edu}}
